An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory (Extended Abstract)

### 2016-07-15 Papers/2016/KI/main.tex

\bibliographystyle{plain}
\bibliography{Bibliography}

>>>>

\bibliographystyle{plain}
%\bibliography{Bibliography}
\begin{thebibliography}{10}

\bibitem{andrewsSEP}
P.B. Andrews.
\newblock Church's type theory.
\newblock In E.N. Zalta, editor, {\em The Stanford Encyclopedia of Philosophy}.
  Spring 2014 edition, 2014.

\bibitem{J23}
C.~Benzm{\"u}ller and L.C. Paulson.
\newblock Quantified multimodal logics in simple type theory.
\newblock {\em Logica Universalis}, 7(1):7--20, 2013.

\bibitem{J30}
C.~Benzm{\"u}ller, L.C. Paulson, N.~Sultana, and F.~Thei{\ss}.
\newblock The higher-order prover {LEO-II}.
\newblock {\em Journal of Automated Reasoning}, 55(4):389--404, 2015.

\bibitem{C40}
C.~Benzm{\"u}ller and B.~Woltzenlogel-Paleo.
\newblock Automating {G\"{o}del's} ontological proof of {God}'s existence with
  higher-order automated theorem provers.
\newblock In Torsten Schaub, Gerhard Friedrich, and Barry O'Sullivan, editors,
  {\em ECAI 2014}, volume 263 of {\em Frontiers in Artificial Intelligence and
  Applications}, pages 93 -- 98. IOS Press, 2014.

\bibitem{CSR}
C.~Benzm{\"{u}}ller and B.~Woltzenlogel~Paleo.
\newblock Interacting with modal logics in the coq proof assistant.
\newblock In Lev~D. Beklemishev and Daniil~V. Musatov, editors, {\em Computer
  Science - Theory and Applications - 10th International Computer Science
  Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July 13-17, 2015,
  Proceedings}, volume 9139 of {\em LNCS}, pages 398--411. Springer, 2015.

\bibitem{C55}
C.~Benzm{\"u}ller and B.~Woltzenlogel~Paleo.
\newblock The inconsistency in {G{\"o}del's} ontological argument: A success
  story for {AI} in metaphysics.
\newblock In {\em IJCAI 2016}, 2016.

\bibitem{Nitpick}
J.C. Blanchette and T.~Nipkow.
\newblock Nitpick: A counterexample generator for higher-order logic based on a
  relational model finder.
\newblock In {\em ITP 2010}, number 6172 in LNCS, pages 131--146. Springer,
  2010.

\bibitem{FitelsonZalta}
B.~Fitelson and E.~N. Zalta.
\newblock Steps toward a computational metaphysics.
\newblock {\em J. Philosophical Logic}, 36(2):227--247, 2007.

\bibitem{GoedelNotes}
K.~G\"odel.
\newblock {\em Appx. A: Notes in Kurt G\"odel's Hand}, pages 144--145.
\newblock In Sobel \cite{sobel2004logic}, 1970.

\bibitem{homl}
R.~Muskens.
\newblock {Higher Order Modal Logic}.
\newblock In P.~Blackburn~et al., editor, {\em Handbook of Modal Logic},
  Studies in Logic and Practical Reasoning, pages 621--653. Elsevier,
  Dordrecht, 2006.

\bibitem{oppenheimer11}
P.E. Oppenheimer and E.N. Zalta.
\newblock A computationally-discovered simplification of the ontological
  argument.
\newblock {\em Australasian J. of Philosophy}, 89(2):333--349, 2011.

\bibitem{sep-ontological-arguments}
G.~Oppy.
\newblock Ontological arguments.
\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Spring 2015 edition, 2015.

\bibitem{rushby13}
J.~Rushby.
\newblock The ontological argument in {PVS}.
\newblock In {\em Proc.~of CAV Workshop ``Fun With Formal Methods''}, St.
  Petersburg, Russia, 2013.

\bibitem{ScottNotes}
D.~Scott.
\newblock {\em Appx. B: Notes in Dana Scott's Hand}, pages 145--146.
\newblock In Sobel \cite{sobel2004logic}, 1972.

\bibitem{sobel2004logic}
J.H. Sobel.
\newblock {\em Logic and Theism: Arguments for and Against Beliefs in God}.
\newblock Cambridge U. Press, 2004.

\bibitem{J22}
G.~Sutcliffe and C.~Benzm{\"u}ller.
\newblock Automated reasoning in higher-order logic using the {TPTP THF}
  infrastructure.
\newblock {\em J. of Formalized Reasoning}, 3(1):1--27, 2010.

\bibitem{Wang1996}
H.~Wang.
\newblock {\em A Logical Journey: From G\"odel to Philosophy}.
\newblock MIT Press, 1996.

\end{thebibliography}
